### 2020-08-01 firmware/eppenwolf/protocols/pulse_1.nw.tex
Noweb -> pweave

import device_comms
import sweep

@@

Avoid any ambiguity regarding the temperature rise seen in the

\nwenddocs{}\nwbegindocs{2}\nwdocspar
Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the Eppenwolf firmware using literate programming.

}

\nwenddocs{}\nwbegincode{3}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
alalsdjkf

test()
BASE_BIAS_GAINaa
aa

\nwendcode{}\nwbegindocs{4}aaaaaaaaaaaa

aaaaaaaaaaaaa

@@

# For each of the animal and human published studies, four
# predetermined and specific quality control measures were used to
# assess the quality of the publication.
# 1. Whether or not the researchers have used ‘‘blind’’ evaluations to
# avoid individual ‘‘bias’’, B or nB;
# 2. Whether or not there was detailed/adequate description of
# ‘‘dosimetry’’ in the publication for independent replication/
# confirmation studies, D or nD.
# 3. Whether or not ‘‘positive controls’’ were included in the
# experiment(s) to replicate/confirm the observations, P or nP.
# 4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
# compare with the observations made in RF exposure conditions)
# were included in the experiments, S or nS. However, it was not our
# intention to ‘‘rank’’ the publications either to exclude or include
# the reported data in the meta-analysis.

>>>>

\clearpage
{\Large \it Experiment 2:}\\

@@

\begin{itemize}
\item Crudely test the pulse hypothesis. \cite{Efficient2015}'s use of a 15 minute exposure caused us some consternation.
    While T4 is quite unlike enveloped viruses, it at least provides a first approximation.
\item Avoid any ambiguity regarding the temperature rise seen in the previous paper.
\end{itemize}

In the end, performing this was a mistake; but by the time we realized this we had already put in the bulk of the time.

Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the {\it Eppenwolf} firmware using \cite{Noweb}.

<<pulse_1.py>>
import device_comms
import sweep

\nwenddocs{}\nwbegindocs{2}\nwdocspar

@@

For each of the animal and human published studies, four
predetermined and specific quality control measures were used to
assess the quality of the publication.
1. Whether or not the researchers have used ‘‘blind’’ evaluations to
avoid individual ‘‘bias’’, B or nB;
2. Whether or not there was detailed/adequate description of
‘‘dosimetry’’ in the publication for independent replication/
confirmation studies, D or nD.
3. Whether or not ‘‘positive controls’’ were included in the
experiment(s) to replicate/confirm the observations, P or nP.
4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
compare with the observations made in RF exposure conditions)
were included in the experiments, S or nS. However, it was not our
intention to ‘‘rank’’ the publications either to exclude or include
the reported data in the meta-analysis.
